Supplemental Materials

### 2021-06-21 supplement/supplement-main.Rmd
refactored

# this is the favorite son (most likely)
main_model <- hc(train, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1e3, restart=5)

@@

```{r}
## NOTE: I just can't figure out how to nicely display the graph and legend in code
## it's must easier just to export them both and then combine with a graphics app

>>>>

# this is the favorite son (most likely)
main_model <- hc(train, blacklist=theory_bl, score="custom", fun=cog_model_score_func, maxp=5, max.iter=1e3, restart=5)
```

@@

```{r}
## NOTE: I just can't figure out how to nicely display the graph and legend in code
## it's easier just to export them both and then combine with a graphics app
